Methods to prioritise pop-up active transport infrastructure

### 2020-06-02 article.Rmd
Close #66

---
title: "Methods to prioritise pop-up active transport infrastructure"
# : overview and findings from 10 UK cities"
author: "Robin Lovelace, Malcolm Morgan, Joey Talbot, Martin-Lucas-Smith"
# output: bookdown::github_document2
# output: bookdown::html_document2
output:
  bookdown::pdf_document2:
    keep_tex: true
# bibliography: references.bib
bibliography: ref.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE, out.width = "100%")
```

@@

```{r load}
library(sf)
library(tidyverse)
library(tmap)
if(!file.exists("rsf_leeds.Rds")) {
  u = "https://github.com/cyipt/tempCycleways/releases/download/0.1/rsf_leeds.Rds"
  download.file(u, "rsf_leeds.Rds")
}
r_original = readRDS("rsf_leeds.Rds")
if(!file.exists("rtid.csv")) {
  ur = "https://github.com/cyipt/tempCycleways/releases/download/0.1/rtid.csv"
  download.file(ur, "rtid.csv")
}
rtid = readr::read_csv("rtid.csv")
# uh = "http://media.nhschoices.nhs.uk/data/foi/Hospital.csv"
# download.file(uh, "uh.csv")
h = readr::read_delim("uh-edited.csv", delim = "|")
# nrow(h) # 1221 hospitals
h_clean = h %>% 
  mutate(Longitude = as.numeric(Longitude)) %>% 
  mutate(Latitude = as.numeric(Latitude)) %>% 
  filter(!is.na(Longitude)) %>% 
  filter(!is.na(Latitude))
hsf = h_clean %>% st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326)
region = ukboundaries::leeds
tmap_mode("plot")
```

>>>>

---
title: "Methods to prioritise pop-up active transport infrastructure"
# : overview and findings from 10 UK cities"
author: "Robin Lovelace, Malcolm Morgan, Joey Talbot, Martin-Lucas-Smith"
# output: bookdown::github_document2
# output: bookdown::html_document2
# output:
#   bookdown::pdf_document2:
#     keep_tex: true
# bibliography: references.bib
bibliography: ref.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = FALSE, out.width = "100%")
```

@@

```{r load}
library(sf)
library(tidyverse)
library(tmap)
region_name = "West Yorkshire"
source("code/build.R")
if(!file.exists("rsf_leeds.Rds")) {
  u = "https://github.com/cyipt/popupCycleways/releases/download/0.1/rsf_leeds.Rds"
  download.file(u, "rsf_leeds.Rds")
}
r_original = readRDS("rsf_leeds.Rds")
if(!file.exists("rtid.csv")) {
  ur = "https://github.com/cyipt/popupCycleways/releases/download/0.1/rtid.csv"
  download.file(ur, "rtid.csv")
}
rtid = readr::read_csv("rtid.csv")
# uh = "http://media.nhschoices.nhs.uk/data/foi/Hospital.csv"
# download.file(uh, "uh.csv")
h = readr::read_delim("uh-edited.csv", delim = "|")
# nrow(h) # 1221 hospitals
h_clean = h %>% 
  mutate(Longitude = as.numeric(Longitude)) %>% 
  mutate(Latitude = as.numeric(Latitude)) %>% 
  filter(!is.na(Longitude)) %>% 
  filter(!is.na(Latitude))
hsf = h_clean %>% st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326)
region = ukboundaries::leeds
tmap_mode("plot")
```
